New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification

### 2025-06-26 experiment.tex
Add new figure

\begin{itemize}
\item[a)] Which non-parametric coupling methods shows good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric method Bayes covariant method which  matches its performance?
\item[c)] If the answer to b) is negative, is it better to apply the change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
\end{itemize}

@@

The first question is whether for some coupling method the difference in predictions between $\boldsymbol{c}_1$ and $\boldsymbol{c}_2$ would be smaller. The results are shown in Table \ref{tab:exp4}.

\input tab-exp4.tex

The second question is whether a coupling method would more consistently provide true answers. Let us remark that Assumption 1 is inconsistent with ground truth being certain. But we may

>>>>

\begin{itemize}
\item[a)] Which coupling methods without parameters show good performance across diverse data sets? Is it the orthodox method of Wu-Lin-Weng?
\item[b)] If the answer to a) is a coupling method which is not Bayes covariant, can we find a parametric Bayes covariant method which  matches its performance?
\item[c)] If the answer to b) is negative, is it better to apply the change of priors before or after coupling? Additionally, how serious is the impact of the lack of Bayes covariance in practice?
\end{itemize}

@@

The first question is whether for some coupling method the difference in predictions (we call it \emph{spread}) between $\boldsymbol{c}_1$ and $\boldsymbol{c}_2$ would be smaller. To gauge this question we apply change of priors by increasing tenfold the prior for every class in turn.  The averaged results are shown in Table \ref{tab:exp4}.

\input {tab-exp4.tex}

The results, as expected, detect no change between $\boldsymbol{c}_1, \boldsymbol{c}_2$ for normal coupling method. However, there is no consistent difference in spread between radial and Wu-Lin-Weng's coupling method. Spread for the radial method is lower for 3 datasets (letter, mnist, usps datasets), higher for 3 datasets (dna, satimage, segment) and tied for waveform dataset.

The second question is whether a coupling method would more consistently provide true answers. Let us remark under Assumption 1 the Bayes classifier \emph{should} change prediction of any sample if the change of priors is sufficiently large. Thus to evaluate this question

\begin{figure}[!ht]
	\includegraphics{exp4-truth.pdf}
	\caption{Difference in accuracies of $\boldsymbol{c}_2$ and $\boldsymbol{c}_1$ for radial and Wu-Lin-Weng's coupling method.}
	\label{fig:score}
\end{figure}
